\vfill LiteCrypto

### 2014-12-12 paper/paper.tex
Added Our Work section. Added references to bibilography. Set margins to 1in. Bibilography page not showing though

%%% PAGE DIMENSIONS
\usepackage[top=4.5cm, bottom=4.5cm, left=2cm, right=2cm]{geometry}
\usepackage{geometry} % to change the page dimensions
\geometry{letterpaper}

@@

Our library should allow any user to have the option to encrypt or authenticate their packets. It should have 3 functions: No security, one way authentication, and authenticated encryption. Using the diagram below is how Dr. Bellardo described how we should encrypt and authenticate. \\

@@

We were told to only encrypt the data portion of the packet, and only authenticate the IPv4 and UDP headers along with the data.

@@

\section{Our Work}

@@

\end{multicols}
\end{document}

>>>>

%%% PAGE DIMENSIONS
\usepackage[margin=1in]{geometry}
\geometry{letterpaper}

@@

Our library should allow any user to have the option to encrypt or authenticate their packets. It should have 3 functions: No security, one way authentication, and authenticated encryption. Using the diagram on the next page is how Dr. Bellardo described how we should encrypt and authenticate. We were told to only encrypt the data portion of the packet, and only authenticate the IPv4 and UDP headers along with the data.

@@

@@

\section{Our Work}
\subsection{Key Exchange}

The LiteCrypto library revolves around symmetric key cryptography. The keys used for authentication and encryption in the LiteCrypto library are pre-shared (or secret) keys. The library expects a key to be provided for all cryptographic functions. In the context of the CubeSat, encryption and authentication keys need to be agreed upon before sending the device for launch into space. Since the LiteCrypto library only provides for cryptographic functions for satellite communications via AX.25/IPv4, the security of the keys in memory or disk used for the library is considered outside the realm of this project. Therefore, we assume the keys used for this library is appropriately secured by another system.

\subsubsection{Tradeoffs Made}

We decided not to perform public-key cryptography because we believed it would have been too much overhead for the CubeSat. The amount of data to be inserted into the packets would have been increased. However, TweetNaCl offers public-key cryptographic functions \cite{TweetNaClPaper}, so it is possible to easily implement public-key cryptography in LiteCrypto.

\subsection{Authentication}

Authentication in LiteCrypto utilizes NaCl library's HMAC-SHA512-256 authentication function. \footnote{TweetNaCl did not provide the function, so we ported the function from the full NaCl library over into the TweetNaCl source files for our use.} The HMAC-SHA512-256 authentication scheme essentially performs HMAC-SHA512 and truncates to the first 256 bits \cite{NaClSiteAuth}. This scheme is conjectured to meet the standard notion of unforgeability \cite{NaClSiteAuth}.

The sign function takes in a 32-byte key \cite{NaClSiteAuth} and variable-length IPv4 packet to output a signed IPv4 packet which has a 32-byte tag \cite{NaClSiteAuth} inserted in the head of the data portion. \footnote{Because we did get to perform live testing, we are unsure if this insertion breaks the IPv4 system. An alternative process for inserting the tag is possible.} The verify function takes a signed IPv4 packet and removes the inserted tag from the head of the data portion. Verification is then performed on the reconstructed packet by generating a new tag to compare with the provided tag. Based on the source files, the comparison in TweetNaCl is done by a constant-time string comparison function to avoid creating side-channels. If the packet verifies, the function outputs the new size of the reconstructed packet. Otherwise, it outputs -1 as ⊥.

\subsubsection{Tradeoffs Made}

We chose HMAC-SHA512-256 over TweetNaCl's one-time authentication because we wanted to be able to reuse the keys. With one-time authentication scheme, reusing a key to authenticate more than one message reveals enough information to allow for forgeries \cite{NaClSiteOneTimeAuth}.

\subsection{Encryption}

LiteCrypto utilizes TweetNaCl's secret-key encryption scheme based on xsalsa20 for encryption. The xsalsa20 scheme expands the amount of nonce bytes available to use for salsa20 \cite{TweetNaClPaper}. Because xsalsa20 uses salsa20 as the core, the security of xsalsa20 depends on the security of the salsa20 scheme \cite{TweetNaClPaper}. The xsalsa20 encryption scheme is conjectured to meet the standard notion of unpredictability \cite{NaClSiteStream}.

The TweetNaCl encryption function generates a key stream from xsalsa20 using a 32-byte key and a 24-byte nonce \cite{NaClSiteStream}, so it effectively acts as a stream cipher \cite{TweetNaClPaper}. The key stream is deterministic in that the same key and nonce pair will generating the same key stream. The key stream is bitwise XORed with the plaintext to produce the ciphertext \cite{TweetNaClPaper}. Note that the encryption scheme does not hide the length of the message \cite{NaClSiteStream}. Because the function acts as a stream cipher, the function can be used both to encrypt or decrypt. We base our encryption function around the use of TweetNaCl's function.

The encrypt function takes in a 32-byte key \cite{TweetNaClPaper} and a variable-length IPv4 packet to output a IPv4 packet with 24-byte nonce inserted at the head of the encrypted data. The IPv4 packet headers are left untouched in plaintext. The nonce is randomly generated by the function by reading from urandom. The NaCl group supports that the “nonces are long enough that randomly generated nonces have negligible risk of collision.” \cite{NaClSiteStream} The size of the encrypted packet is returned on success; otherwise, -1 is returned.

The decrypt function takes in a 32-byte key \cite{TweetNaClPaper} and a variable-length encrypted IPv4 packet to output a decrypted IPv4 packet with the nonce bytes removed. The nonce bytes are removed from the head of the encrypted data of the given encrypted packet. The encrypted data is then decrypted using the provided key and nonce bytes. We construct the new packet by appending the decrypted data to the IPv4 headers. The size of the decrypted packet is returned on success; otherwise, -1 is returned.

\subsection{Authenticated Encryption}

Authenticated encryption in LiteCrypto makes use of the authentication and encryption functions discussed above. To encrypt a packet, we first perform our encryption scheme then our authentication scheme. We have ultimately inserted 56 bytes into the IPv4 packet: 32 bytes from authentication tag and 24 bytes from encryption nonce. To decrypt, we first attempt to verify the packet. If the packet verifies, we perform our decryption scheme and output the decrypted packet without the 56 bytes originally inserted; otherwise, -1 is outputted as ⊥. Our encrypt-sign and verify-decrypt schemes achieve authenticated encryption by never decrypting a non-authenticated packet.

Because we have intermediate states between encrypt-sign and verify-decrypt, we have dynamically allocated memory to contain the intermediate states. On memory allocation error, the function returns -1. Having the dynamically allocated memory does not decrease the security of LiteCrypto since the intermediate states only contain the IPv4 header which is left in plaintext at all times, the nonce bytes, and the encrypted data. An adversary would not gain any more information than if he or she caught an encrypted packet.

\subsection{PBKDF2}

The keys used for authentication and encryption in LiteCrypto are expected to be 32 bytes long. For the users' convenience, we have included a specialized password-based key-derivation function for this library. The function takes in two user provided parameters: a variable-length key and a 16-byte salt. The function outputs a 32-byte key to the specified location and returns the size of the key on success. On failure, the key-derivation function returns -1.

The key-derivation scheme follows the standard PBKDF2 scheme from \cite{PBKDF2Standard} with SHA512 as the underlying pseudo-random function. Since SHA512's digest size is 64 bytes \cite{NaClSiteHash} and our required key size is only 32 bytes, we only have one block under the PBKDF2 scheme. Because we always have only one block, we have omitted the block number from the initial iteration in evaluating U1 of the block. Excluding U1 which uses the user-provided salt, we perform ten thousand iterations with each iteration using the previous iteration's output as salt on the user-provided key \cite{PBKDF2Standard}. All iterations are then bitwise XORed together to form the output key \cite{PBKDF2Standard}.

@@

\clearpage
%cite all the references from the bibtex you haven't explicitly cited
\nocite{*}
%break long urls with lots of hyphens
\def\UrlBreaks{\do\/\do-}

\bibliographystyle{IEEEannot}

\bibliography{paper}
\end{multicols}
\end{document}
